---
title: "ANLY512 Assignment 4"
author: "Tianhe Wang"
date: "03/05/2019"
output: 
        html_document:
                code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(ggplot2);library(rgdal);library(leaflet);library(dplyr);library(htmltools);library(tidyr)
# other code here to set-up your data file
setwd("D:\\Work\\HU\\dataviz\\assignment4")
allSchools <- read.csv("EasternSchools.csv", quote = "\"", header = TRUE)
school_lvl1<- allSchools[which(allSchools$LEVEL==1), ]
school_lvl2<- allSchools[which(allSchools$LEVEL==2), ]
school_lvl3<- allSchools[which(allSchools$LEVEL==3), ]
school_lvl4<- allSchools[which(allSchools$LEVEL==4), ]
zips<-readOGR(dsn="./cb_2017_us_county_500k",layer="cb_2017_us_county_500k") # no file extension!
counties <- readOGR(dsn="./Pennsylvania_School_Districts",layer="cb_2016_42_unsd_500k")
```

### Purpose

This assignment includes a dataset containing information of randomly selected 700 public schools (around 3000 in total) in the eastern area of Pennsylvania. It shows some schools characteristics of the schools, such as geographic information, population of the students or grades of the student, etc. These offers many different dimensions and hints to show many interesting phenomonens in this Philadelphia area. In my report, I may emphasis on the races, as an international student , I would like to know about how different races behaves in these school? Which level os school that has the most non-native? Or even after graduation, how these students go?

### Methodology

For the questions I have brought along with the report (mentioned in 'Purpose' section). I need to pick up some data I am really interested in. Data such as Race, Grades, School Category, Location. And show it up on map since the area information matters in my analysis.


### Analysis
The first thing I do here is to have an overview of the distribution of the schools in Philadelphia area. Normally a school has a certainly level range. Having inspected the dataset and internet, the higher levels of schools indicates higher education levels. Levels are from pre kindergarten, kindergarten, G01 to G13. Level 1 school covers all levels up to G06, sometimes G04 or G05. Level 2 school covers levels from G04 to G06, Level 3 covers from G07 to G12, Level 4 covers all the way to G13. The distribution of different schools' levels are almost the same. However from the density of school level, we could see that low level schools still take high percentages in schools.

`r plot(2:6,3:7,col='red')`. 

```{r warning=FALSE, message=FALSE}
lvl1_schools = leaflet() %>% addTiles() %>% 
                  addCircleMarkers(data=school_lvl1,lng=~LON,lat=~LAT, 
                                   radius = 3, color="red", fillColor = "red")
lvl2_schools = leaflet() %>% addTiles() %>% 
                  addCircleMarkers(data=school_lvl2,lng=~LON,lat=~LAT, 
                                   radius = 3, color="yellow", fillColor = "yellow")
lvl3_schools = leaflet() %>% addTiles() %>% 
                  addCircleMarkers(data=school_lvl3,lng=~LON,lat=~LAT, 
                                   radius = 3, color="blue", fillColor = "blue")
lvl4_schools = leaflet() %>% addTiles() %>% 
                  addCircleMarkers(data=school_lvl4,lng=~LON,lat=~LAT, 
                                   radius = 3, color="green", fillColor = "green")

leaflet_grid <- 
  tagList(
    tags$table(width = "100%",
         tags$tr(
           tags$td(lvl1_schools),
           tags$td(lvl2_schools)
         ),
         tags$tr(
           tags$td(lvl3_schools),
           tags$td(lvl4_schools)
         )
    )
  )

browsable(leaflet_grid)

```
Now lets emphasize on Level 1 school since we could see that level 1 school has the most people in Philadelpha area, which is more representative. From observation, all level 1 school cover G01 grade. I am trying to show the average grades' distribution of G01. By comparing the two rectangles, we could see that the location does matter on grades. Even though more school means deeper color density and overlapping thing may affect the grades' opacity. Students who lives nearby larger city has higher grades.

```{r warning=FALSE, message=FALSE}
grades01 = school_lvl1$G01

G01_grades = leaflet() %>% addTiles() %>%
  addCircleMarkers(data = school_lvl1, radius = 1.5, fill = FALSE, color = "red", opacity = (grades01-20)/100,
                   lng=~LON, lat=~LAT) %>%
  addRectangles(lng1 = -74.90000, lat1 = 40.10000, lng2 = -75.40000, lat2 = 40.35000, color = "black", weight = 5,
                fillColor = "transparent") %>%
  addRectangles(lng1 = -75.70000, lat1 = 40.50000, lng2 = -75.10000, lat2 = 40.75000, color = "black", weight = 5,
                fillColor = "transparent")
G01_grades

```

Would school categories affect students grades? The answer is no.

```{r warning=FALSE, message=FALSE}
m_school = allSchools %>% filter(magnetSchoolStatus == "Yes")
c_school = allSchools %>% filter(isCHARTER == "Yes")

school_grade = leaflet(counties) %>% addTiles() %>%
  addPolygons(weight=1,color="blue",fillOpacity = .1) %>%
  addCircleMarkers(data = m_school, radius = 2, color = "yellow", weight = 3, opacity = (grades01)/100, label = ~city) %>%
  addCircleMarkers(data = c_school, radius = 2, color = "blue", weight = 3, opacity = (grades01)/100, label = ~city) %>%
  addLegend("topright", colors = c("red", "green"), labels = c("magnet school", "charter school"), title = "Type of School", opacity = 1)
school_grade
```

At last as an international from China, I would love to see on all levels aspects, which area/schools that Asians want to go most.
```{r warning=FALSE, message=FALSE}
asians = leaflet() %>% addTiles() %>% 
  addCircleMarkers(data=allSchools,lng=~LON,lat=~LAT, 
                   radius = 3, opacity = allSchools$raceASIAN / 100, color="purple", fillColor = "purple")
asians
```

### Results & Conclusion
In this report, I emphasize on the location, grades and races to see if these factors has any correlations between them. In larger city students are tending to behave well, at least from my inspection, students (grade 01) behave better in Philadelphia area than Allentown. However, I only compared grade 01. In the future work, I would list all level of grades to expand my research. 


